{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-11-30 wacv_for_review.tex
another stretch.

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. This is primarily because
most of embedded systems come with an image acquisition pipeline, and
a tremendous amount of progress on computer vision research has been
made for the past few decades. However, to successfully deploy a
computer vision algorithm on any existing embedded system, a vision
algorithm needs to satisfy, at least, two criteria with the assumption
of reasonably good performance: minimal, manual intervention after
deployment and small footprint of consuming computational
resources. To develop a single-target tracking algorithm that
satisfies these criteria, we propose an ensemble of the kernelized
correlation filters (KCF), we call it {\it E}nKCF. A committee of KCFs
is specifically designed to address the scale-change and dynamic
maneuver of the target over frames. In particular, to guarantee a
high-speed run-time performance, we deploy each of KCFs in turn,
instead of applying multiple KCFs to each frame. To minimize any
potential drifts between individual KCFs' transition, we developed a
Bayes filter. Experimental results showed that the performance of ours
is, on average, 70.10\% for precision at 20 pixels, 53.00\% for
success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
data. The results showed that our method is better than other
high-speed trackers over 5\% on precision on 20 pixels and 10-20\% on
AUC on average. Moreover, our implementation ran at 340 fps for OTB100
and at 416 fps for UAV123 dataset that is faster than DCF (292 fps)
for OTB100 and KCF (292 fps) for UAV123. To increase flexibility of
the proposed {\it E}nKCF running on various single-board computers,
particularly ones with GPUs, we also explored different levels of deep
convolutional features.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a monocular camera. Instead of just manually being
flew for video recording, an unmanned air vehicle (UAV) equipped with
an object or feature following functionality would make it more useful
in the application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

\begin{figure*}[!h]
\centering
\includegraphics[width=\textwidth]{./figures/ResultsIntroduction.pdf}
\caption{Examples of tracking results (yellow rectangles) by the
  proposed method on the ``UAV123'' dataset. This ``UAV123'' dataset
  is challenging for object tracking as a target's scale is changed
  drastically in a few frames.}
\label{ResultsIntroduction}
\end{figure*}

In this paper, we propose a single-target tracking algorithm that does
not require offline training and can run on any embedded or mobile
platforms. Specifically, we would like to make our algorithm 1) learn
the appearance model of a target on the fly and 2) run as fast on a
typical desktop as up to $300$-$450$ fps, aiming at running, at least,
faster than 30 fps when it is deployed on a low-end, embedded
system.\footnote{In general, it would not be easy to compare run-time
  performance of a computer vision algorithm running on an Intel or
  AMD desktop or a laptop and on that (e.g., ARM) of a single-board,
  embedded system. This is primarily due to the difference in their
  architectures and available computing resources. To derive these
  numbers (``300'' and ``30'' fps), we assume that there is roughly an
  1/10th scale down of computational resources from a typical PC to an
  embedded system. We found such a scale-down in computation based on
  exemplar processors, e.g., Intel's i7 quad-core vs ARMv8 dual-core.}

@@

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like any other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a form of the
circulant matrix \cite{henriques2015high}. One can optimally solve
this regression problem using a ridge regression in a closed
form. However, this solution has to deal with expensive matrix
operations $\mathcal{O}(n^{3})$. The correlation filter offers a less
complex solution, $\mathcal{O}(n\log n)$ over element-wise
multiplication in a frequency domain
\cite{bolme2010visual,henriques2015high}. Thank to this reformulation,
an object tracking pipeline based on the correlation filter can run
very efficiently and be even easily implemented. In fact, an extension
of a linear correlation filter, the kernelized correlation filter with
multi-channel features \cite{henriques2015high} showed impressive
object tracking results and outperformed other state-of-the-art,
online tracking algorithms in terms of run-time and tracking
accuracy. However, a vanilla form of such an online tracker is prone
to drift, and fails to track a target over a long period of time
\cite{henriques2015high}. This is primarily due to the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train,
unless a compromise on the frequency of updating the model is
carefully implemented \cite{santner2010prost}. For example, one may
handle a target's scale variation by just concatenating multiple
correlation filters including KCF and running them on each
frame. Alternatively one could think of scanning the region of
interest (ROI) with a list of templates in predefined scale ratios to
find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple KCF on each frame.

@@

The contribution of this paper is a novel, single-target tracking
algorithm running in a very high-speed ($\geq300$ fps). In particular,
to effectively address the changes in scale and translation of a
target, the proposed algorithm deploys each of three, special-purpose
KCFs in turn. Because of such a deployment strategy, the run-time
performance of the proposed algorithm perserves high. To minimize any
potential drifts while switching KCFs, we developed a Bayes filter. In
addition, to increase the flexibility of the proposed algorithm's
usage, we explore deep convolutional features with varying levels of abstraction to boost 
tracking performance.

@@

\begin{comment}
Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.
\end{comment}

\begin{figure*}[!h]
\centering
\includegraphics[width=1\textwidth]{./figures/LearnedFiltersComparison2.pdf}
\caption{This figure shows that there is a marginal difference among
  the scale filters learned either at every frame or at every 5
  frames. The sub-figures at the the left show the scale filters
  trained at every frame and those at the right show the scale filters
  trained at every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure*}

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides the translation filters
, $R_{t}^{L}$ and $R_{t}^{S}$, more accurate ROIs. On the other hand, 
a translation filter, $R_{t}^{L}$, is designed to look at a larger search 
area to estimate the target's translation and recover from any potential 
drifts. Another translation filter, $R_{t}^{S}$, is designed to address the drawback of
$R_{t}^{L}$ that it may learn noisy shape features due to its relatively larger
search area. In what follows, we will detail the main idea behind the
KCF.

@@

\begin{comment}
In practice, the solution vector, $\mathbf{\hat{\alpha}}$, and 
the feature template matrix, $\mathbf{x}$, are accumulated over time
to integrate temporal information as
\begin{align}
 \mathbf{\hat{\alpha}_{t}} =  (1 - \beta)  \mathbf{\hat{\alpha}_{t-1}} +  \beta \mathbf{\hat{\alpha}_{t}} \\
  \mathbf{x_{t}} =  (1 - \beta)  \mathbf{x_{t-1}} + \beta  \mathbf{x_{t}}
\end{align}

where $\beta$ is the learning rate and mostly tuned to a small value.
\end{comment}

In the following sections, we will detail two different types of
features used in {\it E}nKCF : (1) hand-crafted features (fHoG +
color-naming) and (2) deep convolutional features.

@@

We use both fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} for the large area translation filter,
$R_{t}^{L}$. This is because the fHoG applied to relatively larger
area tends to be noisier and less discriminative and adding color
information makes the feature vector for the translation filter 
more discriminative. Figure \ref{fig:Filters}(b) shows an example of 
this translation filter. But, this is not the case for the small area 
translation filter, $R_{t}^{S}$, because it contains relatively smaller background area. 
For this reason, the $R_{t}^{S}$ only employs the fHoG features. 
Figure \ref{fig:Filters}(a) shows an example of this
translation filter. Lastly, we use both fHoG and color-naming features
again for the scale filter, $R_{s}$. By assigning fHoG and
color-naming features, we ensure that the likelihood of inaccurate
scale estimation is reduced in comparison to the scale filter with
only fHoG features. This is more important in our case as the scale
filter is operated in every 5 frames in the proposed tracker. Also,
the scale filter, explained earlier in the algorithm \ref{alg:MKCF},
estimates the scale of a target by correlating it with three candidate
ROIs. This search may increase the run-time complexity of the scale
filter from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$. To
ensure actual filtering operations practical, we use a smaller
template size (i.e., 64$\times n$) for the scale filter, $R_{s}$. The
smaller template size does not degrade the tracking performance
because of 1) zero padding around the target (smaller ROI) and 2) use
of color-naming features.

\textbf{{\it E}nKCF with Deep Convolutional Features} In addition to
hand-crafted features, we explore deep convolutional features to boost tracking
performance. This version of {\it E}nKCF, Deep{\it E}nKCF is designed
to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.
\begin{comment}
{\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}

{\it YoungWoo :
  EnkCF with deep features improved the performance on the same set of
  data.}

{\it Burak: If EnKCF w/ deep features improved the performance of
  EnKCF on the same set of data, why didn't you plot their curves
  together? And if this is true, we'll have to revise the abstract and
  introduction as well!}

  {\it YoungWoo : I compare the EnKCF with all the other trackers that does not use deep features. For this reason
  it does not make sense to put DeepEnKCF in the same figure (Figure 6). We have a separate section 
  showing how much improvement we get by using deep features and in this section I plot them in the same figure ( Figure (8) ).}

{\it Burak: We can put these together if their performances from the
  same data -- don't need to use the same features to be on the same
  graph! We said EnKCF w/ deep features improved the performance, then
  what's the point to separate them into two graphs?}

{\it YoungWoo : There are three reasons for this: (1) One is CPU and another one is GPU
implementations, I thought it would be more clear to separate them, (2) I do not have 
results on OTB100 dataset with DeepEnKCF. (3) I believe DeepEnKCF is not the main contribution 
of this paper, showing them in the same figure with all the trackers might lead the authors to 
underestimate EnKCF.
 }
\end{comment}

There has been a large volume of studies on utilizing a pre-trained
CNN features in tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to increased translational invariance in this
layer. \cite{ma2015hierarchical} proposed a KCF tracker integrating
features with higher abstraction capacity.  Their method first employs
the third convolutional layer features to estimate the response
map. In the next stage, the KCF, concentrating on the second
convolutional layer features, is run to update transition. The third
KCF then works on the transition given by the previous KCF and learns
the first convolutional layer features to update the transition. This
coarse-to-fine approach accommodates different levels of abstractions
of the object. However, it runs multiple KCFs in a sequential fashion,
increasing the run-time complexity. For this reason, we follow an
approach similar to \cite{danelljan2015convolutional}, in order to
embed deep features in {\it E}nKCF. Our {\it E}nKCF algorithm enables
us to exploit different level of feature encodings with different
KCFs. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider
at least twice bigger area than the scale filter, $R_{s}$. Given this,
we can assign deeper feature encodings to $R_{s}$ as it learns less
spatial information than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign
the activations of the fourth convolutional layer features
($26\times26\times128$) to $R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$
are assigned the activations of the second layer features
($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
this feature assignment. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. The conv222 setting stands for the assignment of
the activations of $2^{th}$ convolutional layer features of VGGNet to
$R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet since it
provides higher spatial resolution at the first several layers than
AlexNet \cite{krizhevsky2012imagenet}.

@@

\textbf{Particle Filter for Smoothing Transition among KCFs}
\begin{comment}
{\it Burak: Does what this section explains still hold good? If what
  this section explains still makes sense, the translation filter,
  $R_{t}^{L}$ doesn't do a good job. Isn't it? If it's not, revise
  this section.}

  {\it YoungWoo : I did not understand what $R_{t}^{L}$ has to do with 
  particle filter}

{\it Burak: Earlier we told the readers why we wanted to have two
  translation filters: one for smaller region, $R_{t}^{S}$, and
  another for larger region, $R_{t}^{L}$. The reason why we have two
  translation filter, instead of one because we wanted to minimize any
  drifts, yes? Read the line from 354 to 374. Then if we say again
  here we have a particle filter for smoothing transition among KCFs,
  they might think those two translation filters do not do their jobs
  well?}

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates the target's scale
at every other $k$ frames. Although the strategy of updating every other 
$k$th frames will result in an optimal run-time performance, this may lead 
drifts at the later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $\mathbf{X_{t}}$, represents the
target's pixel coordinates and its velocity, $\mathbf{X_{t}} = \lbrace
x, y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel
coordinates of the target's centroid, $v_x$ and $v_y$ are the velocities
estimated along the $x$-axis and $y$-axis. The particle filter
predicts, using a constant velocity motion model, the target's next
state by generating a predefined number of particles. Then it uses the
confidence maps of {\it E}nKCF as observation to update its state. The
particle weight is computed as, $w_{p_{t}}(x_{t},y_{t}) =
\sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where
$w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$
and $M$ denote the number of rows and columns of the confidence map.

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate the performance of the proposed {\it E}nKCF tracker and
its variants on the object tracking benchmark
datasets. Particularly, we choose two publicly available datasets:
OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos of 100 objects whereas
UAV123 dataset contains aerial footages of 123 objects.  We first test
the {\it E}nKCF with two hand-crafted features, fHoG and color-naming.
With this version, our goal is to have an object tracking algorithm
that ``efficiently'' runs on an embedded system, a drone, in ``high
speed,'' $\ge 30$ fps. Given this goal, we believe that the UAV123
dataset is a good fit in evaluating the performance of the proposed
algorithm. In addition, in the UAV123 dataset, there are many
challenging, realistic scenes, e.g., abrupt scale/illumination
changes. Although we are primarily interested in developing an
algorithm for mobile, embedded robotic applications, it is also
important to compare the performance of the proposed algorithm with
those of the state-of-the-art in a nominal dataset. To this end, we
chose the OTB100 dataset that contains the videos recorded from smart
phones and typical cameras in perspective view. Also, we tested the
proposed algorithm on a temporally down-sampled version of the UAV123
dataset, called UAV123$\_$10fps dataset. What we would like to
evaluate using this modified dataset is how robust the proposed
algorithm is to the drastic motions of camera and targets. Finally, we
evaluate the Deep{\it E}nKCF, {\it E}nKCF with deep convolutional
features, on the UAV123 dataset to observe how much gain we can
achieve over the hand-crafted features.

\textbf{Finding Optimal Hyper-parameters} As each of three KCFs in
       {\it E}nKCF is designed to address specific challenges in
       single target tracking problem, the optimal parameters for
       individual KCFs should be different. We set the learning rates
       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$
       differently as $0.020$, $0.020$ and $0.010$. For the kernel of
       the Gaussian neighboring function, we empirically found the
       optimal values of $\alpha$ as $0.7$, $0.6$, and $0.9$ for
       $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter
       update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
       ratio. The padding size for the correlation filters is tuned to
       $2$ for $R_{t}^{L}$, $1.50$ for $R_{t}^{S}$, and $0$ for
       $R_{s}$. For our particle filter implementation, we empirically
       set the number of particles to $1,000$ to balance the run-time
       performance and accuracy. To keep the level of variance among
       the particles reasonable, we performed the re-sampling only
       when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
       \approx (\sum_{p=1}^{P}\mathbf{w}_{p}^{2})^{-1} $), is lower than a
       pre-defined threshold.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. For such an application, it
is desirable for the deployed algorithms to run in high-speed and
require no offline training. To develop a single-target tracking
algorithm with these properties, we propose an ensemble of the
kernelized correlation filters (KCF), we call it {\it E}nKCF. A
committee of KCFs is specifically designed to address the variations
in scale and translation of moving objects. To guarantee a high-speed
run-time performance, we deploy each of KCFs in turn, instead of
applying multiple KCFs to each frame. To minimize any potential drifts
between individual KCFs' transition, we developed a particle
filter. Experimental results showed that the performance of ours is,
on average, 70.10\% for precision at 20 pixels, 53.00\% for success
rate for the OTB100 data, and 54.50\% and 40.2\% for the UAV123
data. Experimental results showed that our method is better than other
high-speed trackers over 5\% on precision on 20 pixels and 10-20\% on
AUC on average. Moreover, our implementation ran at 340 fps for the
OTB100 and at 416 fps for the UAV123 dataset that is faster than DCF
(292 fps) for the OTB100 and KCF (292 fps) for the UAV123. To increase
flexibility of the proposed {\it E}nKCF running on various platforms,
we also explored different levels of deep convolutional features.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a monocular camera. Instead of just manually being
flew for video recording, an unmanned air vehicle (UAV) equipped with
an object or feature following function would make it more useful for
the application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

\begin{figure*}[!h]
\centering
\includegraphics[width=\textwidth]{./figures/ResultsIntroduction.pdf}
\caption{Examples of some tracking results (yellow rectangles) by the
  proposed method on the ``UAV123'' dataset. The ``UAV123'' dataset is
  challenging for object tracking as the scale and translation of a
  target can be drastically changed in a few frames.}
\label{ResultsIntroduction}
\end{figure*}

In this paper, we propose a single-target tracking algorithm that does
not require offline training and can run in a
high-speed. Specifically, we would like to have our algorithm 1) learn
the appearance model of a target on the fly and 2) run as fast on a
typical desktop as up to $300$-$450$ fps.

@@

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like any other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a form of the
circulant matrix \cite{henriques2015high}. One can optimally solve
this regression problem using a ridge regression in a closed
form. However, this solution has to deal with expensive matrix
operations $\mathcal{O}(n^{3})$. The correlation filter offers a less
complex solution, $\mathcal{O}(n\log n)$ over element-wise
multiplication in a frequency domain
\cite{bolme2010visual,henriques2015high}. Thank to this reformulation,
an object tracking pipeline based on the correlation filter can run
very efficiently and be even easily implemented. In fact, an extension
of a linear correlation filter, the kernelized correlation filter with
multi-channel features \cite{henriques2015high} showed impressive
object tracking results and outperformed other state-of-the-art,
online tracking algorithms in terms of run-time and tracking
accuracy. However, a vanilla form of such an online tracker is prone
to drift, and fails to track a target over a long period of time
\cite{henriques2015high}. This is primarily due to the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train,
unless a compromise on the frequency of updating the model is
carefully implemented \cite{santner2010prost}. For example, one may
handle a target's scale variation by just concatenating multiple
correlation filters including KCF and running them on each
frame. Alternatively one could think of scanning the region of
interest (ROI) with a list of templates in predefined scale ratios to
find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches would drastically reduce run-time performance because
multiple KCFs run on each frame.

@@

The contribution of this paper is a novel, single-target tracking
algorithm running in a very high-speed ($\geq300$ fps). In particular,
to effectively address the changes in scale and translation of a
target, we extended the KCF and deployed each of three KCFs in
turn. Because of such a deployment strategy, the run-time performance
of the proposed algorithm maintains high without sacrificing the
accuracy of tracking. To minimize any potential drifts while switching
KCFs, we developed a particle filter. In addition, to increase the
flexibility of the proposed algorithm's usage, we explore deep
convolutional features with varying levels of abstraction.

@@

\begin{figure*}[!h]
\centering
\includegraphics[width=1\textwidth]{./figures/LearnedFiltersComparison2.pdf}
\caption{These examples show that there is a marginal difference
  between the scale filters learned at every frame and the one learned
  at every 5 frames. The left, sub-figures show the scale filters
  trained at every frame and those at the right show the scale filters
  trained at every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure*}

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides the translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, with more accurate ROIs. On the other
hand, a translation filter, $R_{t}^{L}$, is devised to look into a
larger search area to estimate the target's translation and recover
from any potential drifts. Another translation filter, $R_{t}^{S}$, is
designed to address the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its relatively larger search area. In what
follows, we will detail the main idea behind the KCF.

@@

In the following sections, we will detail two different types of
features used in {\it E}nKCF: hand-crafted features (fHoG +
color-naming) and deep convolutional features.

@@

We use both fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} for the large area translation filter,
$R_{t}^{L}$. This is because the fHoG applied to relatively larger
area tends to be more noisy and less discriminative, and adding color
information makes the feature vector for the translation filter more
discriminative. Figure \ref{fig:Filters}(b) shows an example of this
translation filter. By contrast, the $R_{t}^{S}$ only employs the fHoG
features because it covers a relatively smaller area.  Figure
\ref{fig:Filters}(a) shows an example of this translation
filter. Lastly, we use both fHoG and color-naming features again for
the scale filter, $R_{s}$. By assigning fHoG and color-naming
features, we ensure that the likelihood of inaccurate scale estimation
is reduced in comparison to the scale filter with only fHoG
features. This is more important in our case as the scale filter is
operated in every 5 frames in the proposed tracker. Also, the scale
filter, explained earlier in the algorithm \ref{alg:MKCF}, estimates
the scale of a target by correlating it with three candidate
ROIs. This search may increase the run-time complexity of the scale
filter from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$. To
ensure actual filtering operations practical, we use a smaller
template size (i.e., 64$\times n$) for the scale filter, $R_{s}$. The
smaller template size does not degrade the tracking performance
because of 1) zero padding around the target (smaller ROI) and 2) use
of color-naming features.

\textbf{{\it E}nKCF with Deep Convolutional Features} In addition to
hand-crafted features, we explore deep convolutional features to
extend the applicability of the {\it E}nKCF and boost tracking
performance.

There has been a large volume of studies on utilizing a pre-trained
CNN features in tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activation of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to increased translational invariance in this
layer. \cite{ma2015hierarchical} proposed a KCF tracker integrating
features with higher abstraction capacity.  Their method first employs
the third convolutional layer features to estimate the response
map. In the next stage, the KCF, concentrating on the second
convolutional layer features, is run to update transition. The third
KCF then works on the transition given by the previous KCF and learns
the first convolutional layer features to update the transition. This
coarse-to-fine approach accommodates different levels of abstractions
of the object. However, it runs multiple KCFs in a sequential fashion,
increasing the run-time complexity. For this reason, we follow an
approach similar to \cite{danelljan2015convolutional}, in order to
embed deep features in {\it E}nKCF. Our {\it E}nKCF algorithm enables
us to exploit different level of feature encodings with different
KCFs. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider
at least twice bigger area than the scale filter, $R_{s}$. Given this,
we can assign deeper feature encodings to $R_{s}$ as it learns less
spatial information than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign
the activation of the fourth convolutional layer features
($26\times26\times128$) to $R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$
are assigned the activation of the second layer features
($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
this feature assignment. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. The conv222 setting stands for the assignment of
the activation of $2^{th}$ convolutional layer features of VGGNet to
$R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet since it
provides higher spatial resolution at the first several layers than
AlexNet \cite{krizhevsky2012imagenet}.

@@

\textbf{Particle Filter for Smoothing Transition among KCFs} As
explained earlier, the {\it E}nKCF updates the target's scale at every
other $k$ frames. Although the strategy of updating every other $k$th
frames will result in an optimal run-time performance, this may lead
drifts at the later frames. To prevent such potential drifts, we
developed a Bayes filter that incorporates a target's motion to smooth
any intermediate outputs from individual KCFs. In particular, we use a
particle filter to estimate the target's image coordinate based on the
{\it E}nKCF's outputs. The state in this paper, $\mathbf{X_{t}}$,
represents the target's pixel coordinates and its velocity,
$\mathbf{X_{t}} = \lbrace x, y, v_{x}, v_{y} \rbrace$, where $x$ and
$y$ are the pixel coordinates of the target's centroid, $v_x$ and
$v_y$ are the velocities estimated along the $x$-axis and
$y$-axis. The particle filter predicts, using a constant velocity
motion model, the target's next state by generating a predefined
number of particles. Then it uses the confidence maps of {\it E}nKCF
as observation to update its state. The particle weight is computed
as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M}
\mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where $w_{p}$ denotes the weight of
the particle $p$ at time $t$, and $N$ and $M$ denote the number of
rows and columns of the confidence map.

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%----------------------------------------------------------------------
So far we explained how the proposed algorithm could efficiently
perform a single-target tracking while effectively addressing
variations in scale and translation of moving objects. To accurately
evaluate the performance of the proposed algorithm in terms of the
goal of this paper, we need data with challenging variations in scale
and translation. To this end, we chose the UAV123
data\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}
that contains 123 video sequences of moving objects captured from
low-altitude UAVs. Because of the nature of the video acquisition --
the targets and the camera are moving together, this data pose a great
deal of challenges as the scale and position of the targets can be
drastically changed in a few frames. To verify that our algorithm is
useful not only for the image data with such extreme challenges but
also for the one with nominal difficulties in single-object tracking,
we also used the OTB100
data\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
that contains the videos recorded from smart phones and typical
cameras in perspective view. In addition, we temporarily down-sampled
the UAV123 data to check how robust our algorithm is to drastic
motions of camera and moving targets. Lastly, we evaluate the proposed
algorithm with deep convolutional features, on the UAV123 dataset to
investigate how much performance gain we can achieve in using deep
features over the conventional features like fHoG and color-naming.

\textbf{Finding Optimal Hyper-parameters} As each of three KCFs in
       {\it E}nKCF is designed to address specific challenges in
       single target tracking problem, the optimal parameters for
       individual KCFs should be different. We set the learning rates
       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as
       $0.020$, $0.020$ and $0.010$. For the kernel of the Gaussian
       neighboring function, we empirically found the optimal values
       of $\alpha$ as $0.7$, $0.6$, and $0.9$ for $R_{t}^{L}$,
       $R_{t}^{S}$, and $R_{s}$. We set the scale filter update
       threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR) ratio. The
       padding size for the correlation filters is tuned to $2$ for
       $R_{t}^{L}$, $1.50$ for $R_{t}^{S}$, and $0$ for $R_{s}$. For
       our particle filter implementation, we empirically set the
       number of particles to $1,000$ to balance the run-time
       performance and accuracy. To keep the level of variance among
       the particles reasonable, we performed the re-sampling only
       when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
       \approx (\sum_{p=1}^{P}\mathbf{w}_{p}^{2})^{-1} $), is lower
       than a pre-defined threshold.
